---
title: "Warped Phillips"
author: "Gavin Martinez"
output:
  pdf_document: default
  html_notebook: default
---

```{r echo = F}
library(jasmines)
library(tidyverse)
```

```{r}
use_seed(7575) %>%
  entity_circle(grain = 10000, size = 1.6) %>%
  unfold_warp(iterations = 100) %>%
  style_ribbon(palette = "viridis", background = "lightblue", alpha = .5)
```

Title: "Warped Phillips"

Artist: Gavin Martinez

Medium: Digital Art (created using the Jasmines R package)

Dimensions: Variable (Digital Display)

Description:

"Warped Phillips" is an intriguing digital artwork created by Gavin Martinez, using the expressive power of the Jasmines R package. This thought-provoking piece showcases Martinez's innovative approach to art, where code and algorithms become the tools for artistic creation.

"Warped Phillips" is centered around a circular form that undergoes a geometrical transformation. Starting as a perfect circle, it gradually warps and distorts, evolving into a Phillips screwdriver shape at the bottom. As the eye moves upward, the shape expands and evolves further into a curved square, creating a dynamic and intriguing visual narrative.

Against a backdrop of a light blue background, the main circular element is bathed in the striking hue of "veridis," a vibrant collection of shades that adds a sense of energy and vitality to the piece. The contrast between the serene background and the vivid colors of the central shape creates a compelling visual tension, drawing the viewer's gaze and sparking curiosity.

#### About the Code

By using the function "entity_circle" I was able to make a circular image the focal point of this piece. By setting grain to 1000 I was able to make a seemingly solid figure instead of a stringy figure displayed by smaller grains. Size effects the point around the circle that the circle stops expanding while "unfold_warp" iterations affect how far out the circle goes from its original form. "style_ribbon" colors the figure with palette and the background with background and controls how transparent the folds in the figure are relative to other parts of the figure using alpha. A higher alpha level results in less transparency and a lower alpha level results in more transparency.
